Manuscript 1 code

### 2024-10-11 manuscript_1_code.Rmd
fixed range on mean synchrony

# calculate mean synchrony within a site (!= synchrony of species at the site level!)
mean_synchrony <- diversity_stability_synchrony %>% 
  group_by(habitat, site) %>% 
  summarise(synchrony_mean = mean(synchrony))

@@

```{r mean synchrony}
mean_synchrony_mod <- glmmTMB(cover_stability ~ synchrony_mean*habitat, family = Gamma("log"), data = dss_spatial_2)
hist(residuals(mean_synchrony_mod)) # chunky
plot(residuals(mean_synchrony_mod) ~ predict(mean_synchrony_mod)) # heteroskedastic
summary(mean_synchrony_mod)
Anova(mean_synchrony_mod)
#                         Chisq Df Pr(>Chisq)    
# synchrony_mean         30.134  1  4.031e-08 ***
# habitat                22.008  3  6.498e-05 ***
# synchrony_mean:habitat 17.251  3  0.0006275 ***
emtrends(mean_synchrony_mod, pairwise ~ habitat, var = "synchrony_mean") # no sig differences but close
# contrast                    estimate   SE  df z.ratio p.value
# Fringing - Backreef            -2.75 1.79 Inf  -1.538  0.4147
# Fringing - Forereef 10m         2.57 1.05 Inf   2.444  0.0691
# Fringing - Forereef 17m         3.73 1.27 Inf   2.946  0.0170
# Backreef - Forereef 10m         5.33 1.85 Inf   2.875  0.0211
# Backreef - Forereef 17m         6.48 1.98 Inf   3.271  0.0059
# Forereef 10m - Forereef 17m     1.15 1.35 Inf   0.853  0.8287
```
```{r plot mean synchrony}
mean_synch_emm <- emmip(mean_synchrony_mod,
                        habitat ~ synchrony_mean,
                        at = list(synchrony_mean = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_mean_synch_effects <- mean_synch_emm %>%
  left_join(dss_spatial_ranges, by = c("habitat")) %>%
  filter(synchrony_mean >= min_spatial_synchrony & 
           synchrony_mean <= max_spatial_synchrony)

>>>>

# calculate mean synchrony within a site (!= synchrony of species at the site level!)
mean_synchrony <- diversity_stability_synchrony %>% 
  group_by(habitat, site) %>% 
  summarise(synchrony_mean = mean(synchrony, na.rm = T))

@@

```{r mean synchrony}
mean_synchrony_mod <- glmmTMB(cover_stability ~ synchrony_mean*habitat, family = Gamma("log"), data = dss_spatial_2)
hist(residuals(mean_synchrony_mod)) # chunky
plot(residuals(mean_synchrony_mod) ~ predict(mean_synchrony_mod)) # fine
summary(mean_synchrony_mod)
Anova(mean_synchrony_mod)
#                         Chisq Df Pr(>Chisq)    
# synchrony_mean         32.914  1  9.634e-09 ***
# habitat                18.523  3  0.0003430 ***
# synchrony_mean:habitat 19.062  3  0.0002654 ***
emtrends(mean_synchrony_mod, pairwise ~ habitat, var = "synchrony_mean") # no sig differences but close
# contrast                    estimate    SE  df z.ratio p.value
# Fringing - Backreef            -3.26 1.503 Inf  -2.166  0.1327
# Fringing - Forereef 10m         2.22 0.995 Inf   2.231  0.1149
# Fringing - Forereef 17m         3.37 1.220 Inf   2.764  0.0291
# Backreef - Forereef 10m         5.48 1.622 Inf   3.377  0.0041
# Backreef - Forereef 17m         6.63 1.769 Inf   3.748  0.0010
# Forereef 10m - Forereef 17m     1.15 1.363 Inf   0.846  0.8322
```
```{r plot mean synchrony}
mean_synch_emm <- emmip(mean_synchrony_mod,
                        habitat ~ synchrony_mean,
                        at = list(synchrony_mean = seq(0,1,0.01)), plotit = F, CIs = T)

filtered_mean_synch_effects <- mean_synch_emm %>%
  left_join(dss_spatial_ranges, by = c("habitat")) %>%
  filter(synchrony_mean >= min_mean_synchrony & 
           synchrony_mean <= max_mean_synchrony)
